Worflow

### 2017-05-30 R/workflow.Rmd
update to RSEC code

```{r}
runZinb = F
runClus = F
NCORES = 2
```

@@

We have `r ncol(counts)` cells.
```{r lookatdata}
dim(core)
core[1:3, 1:3]
```

Cells have been processed in `r length(unique(batch))` different batches
```{r tabbatch}
table(batch)
```

Cells have been clustered into `r length(unique(clus.labels))` different clusters
```{r tabclus}
table(clus.labels)
```

Batches are kind of confounded with the biology
```{r}
table(data.frame(batch = as.vector(batch),
                 cluster = clus.labels))

```

@@

I use the code of Davide from zinb_clutering_over_k.Rmd
```{r consensus_50}
## matching the parameters used by Russell
W = zinb50@W
fn = '../data/clustExp_W_k50.rda'
if(runClus) {
  cl_res <- clusterMany(t(W), ks = 4:15, alphas = c(0.1), betas = 0.8,
                        clusterFunction = "hierarchical01", minSizes=1,
                        sequential = TRUE, subsample = TRUE, ncores = 7,
                        subsampleArgs = list(resamp.num=100,
                                             clusterFunction="kmeans",
                                             clusterArgs=list(nstart=10)),
                        seqArgs = list(k.min=3, top.can=5), verbose=TRUE)
  save(cl_res, file = fn)
} else {
  load(fn)
}
```

@@

Just to see what it looks like, let's look at the heatmap on the W (number of cells x K=50). Now, we would like to plot a heatmap using the residuals (number of cells x number of genes). When I call plotHeatmap using argument visualizeData = residuals_matrix, it does not work and says that if give separate visualizeData, must be of same dimensions as assay(data).
```{r heatmap}
plotHeatmap(merged, clusterSamplesData="dendrogramValue", breaks = .99)
```

>>>>

```{r}
runZinb = FALSE
runClus = FALSE
NCORES = 2
```

@@

We have `r ncol(counts)` cells.

```{r lookatdata}
dim(core)
core[1:3, 1:3]
```

Cells have been processed in `r length(unique(batch))` different batches

```{r tabbatch}
table(batch)
```

Cells have been clustered into `r length(unique(clus.labels))` different clusters

```{r tabclus}
table(clus.labels)
```

Batches are kind of confounded with the biology

```{r}
table(data.frame(batch = as.vector(batch),
                 cluster = clus.labels))
```

@@

EAP: Fanny, we should really be using the RSEC function for all the steps of the clustering. I've put in the code, but I set `eval=FALSE` because I don't have the data to test it. I also am not sure that we want to set the options for `subsampleArgs` and `seqArgs` since those are suppose to be sort of esoteric concerns...

```{r rsec_50, eval=FALSE}
fn = '../data/clustExp_W_k50.rda'
if(runClus) {
ceObj <- RSEC(t(W), k0s = 4:15, alphas = c(0.1), betas = 0.8,
                      clusterFunction = "hierarchical01", minSizes=1,
                      sequential = TRUE, subsample = TRUE, ncores = NCORES,
					  combineProportion = 0.7,mergeMethod = "locfdr", mergeCutoff = 0.01
                      subsampleArgs = list(resamp.num=100,
                                           clusterFunction="kmeans",
                                           clusterArgs=list(nstart=10)),
                      seqArgs = list(k.min=3, top.can=5), verbose=TRUE)
save(ceObj, file = fn)
}
else{
	load(fn)
}
```

```{r examineCombineMany, eval=FALSE}
plotClusters(ceObj, colPalette = c(bigPalette, rainbow(100)))
plotCoClustering(ceObj)
table(primaryClusterNamed(ceObj))
sum(primaryCluster(ceObj) == -1)
```

```{r examineMergeClusters, eval=FALSE}
#re-does merging simpling to make plot 
mergeClusters(ceObj, mergeMethod = "locfdr", plot="mergeMethod",cutoff = 0.01)
```

```{r heatmap,eval=FALSE}
plotHeatmap(ceObj, clusterSamplesData="dendrogramValue", breaks = .99)
```

## Original ClusterExperiment code (in Steps)
I use the code of Davide from zinb_clutering_over_k.Rmd

```{r consensus_50}
## matching the parameters used by Russell
W = zinb50@W
fn = '../data/clustExp_W_k50.rda'
if(runClus) {
  cl_res <- clusterMany(t(W), ks = 4:15, alphas = c(0.1), betas = 0.8,
                        clusterFunction = "hierarchical01", minSizes=1,
                        sequential = TRUE, subsample = TRUE, ncores = 7,
                        subsampleArgs = list(resamp.num=100,
                                             clusterFunction="kmeans",
                                             clusterArgs=list(nstart=10)),
                        seqArgs = list(k.min=3, top.can=5), verbose=TRUE)
  save(cl_res, file = fn)
} else {
  load(fn)
}
```

@@

Just to see what it looks like, let's look at the heatmap on the W (number of cells x K=50). Now, we would like to plot a heatmap using the residuals (number of cells x number of genes). When I call plotHeatmap using argument visualizeData = residuals_matrix, it does not work and says that if give separate visualizeData, must be of same dimensions as assay(data).

```{r heatmap}
plotHeatmap(merged, clusterSamplesData="dendrogramValue", breaks = .99)
```
